---
output: github_document
---

# Iterating with plumber

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Getting your plumber API up and running takes a bit of fiddling around. Rather than launching swagger each time, and testing your arguments manually, you can use the following workflow:

1. Draft your plumber function
2. Run `start_plumber(path, port)`
3. Check that it works as expected using `httr`
4. Fiddle with your plumber function if something is off
5. Repeat 2-4 until you get it right!

If you have ready-built plumber functions, you can use test them out directly in a single RStudio session by opening up a new terminal with `start_plumber`. I've included a two functions (`random_praise` and `random_data`) in a sample plumber file in the `inst` folder of this repo. Depending on what seed you set, the output changes:

```{r eval = FALSE}
# devtools::install_github("isteves/plumbplumb")
library(plumbplumb) 

plumber_path <- system.file("plumber.R", package = "plumbplumb")
start_plumber(plumber_path, port = 8484)

bar <- httr::GET("http://127.0.0.1:8484/random_praise?seed=2")
httr::content(bar, as = "text")

foo <- httr::GET("http://127.0.0.1:8484/random_praise?seed=3")
httr::content(foo, as = "text")
```

Same with the data:

```{r eval = FALSE}
baz <- httr::GET("http://127.0.0.1:8484/random_data?seed=2")
httr::content(baz)

boo <- httr::GET("http://127.0.0.1:8484/random_data?seed=3")
httr::content(boo)
```

